SHARP - II. Beware the effect of edge-on discs when interpreting the anomalous flux-ratios of gravitationally lensed quasars

### 2015-08-31 papers/B1555_EdgeOn/B1555_letter.tex
update of John's draft

%\documentclass[useAMS,usenatbib]{mn2e}
\documentclass[useAMS,usenatbib]{mnras}
%\documentclass[usenatbib]{mn2e}
\usepackage{graphicx}
%\usepackage[nottoc]{tocbibind}
\setlength{\topmargin}{-1.2cm}

% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%

% Journal definitions
%\newcommand{\apj}[1]{ApJ}
%\newcommand{\mnras}[1]{MNRAS}
%\newcommand{\apjl}[1]{ApJL}
%\newcommand{\pasj}[1]{PASJ}
%\newcommand{\aj}[1]{AJ}
%\newcommand{\nat}[1]{Nature}
%\newcommand{\aap}{A\&A}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[Beware the Effect of Edge-on Disks]{
%Gravitational Lens Modelling of flux-ratio Anomalous System B1555+375
SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio
Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on
Disks
}
\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
jwhsueh@ucdavis.edu (JWH); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\\
$^{1}$Physics Dept., University of California, Davis, 1 Shields Ave.
Davis, CA 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

\begin{abstract}

Gravitational lens flux-ratio anomalies provide a powerful technique
for detecting the presence of dark matter substructure in distant
galaxies.  However, before using the statistics of systems with these
anomalies, it is imperative to ascertain that a given system does not
have properties that could plausibly cause the observed anomaly
without the need for substructure.  In this letter, we present the
case of the B1555+375 lens system, which has a strong radio-wavelength
flux-ratio anomaly but where the lensing galaxy is also revealed in
high-resolution infrared imaging to have a clear edge-on disk component.  The
disk crosses directly over the pair of images that exhibit the
anomaly, and we show that simple models that include the disk can
reproduce the anomaly without requiring substructure.  
%Other lens systems that we have observed with adaptive optics imaging
%as part of the Strong lensing at High Angular Resolution Programme (SHARP)
%show a similar behaviour and will be the subject of a future paper.  
These results suggest that the assumption that
all flux-ratio anomalies are due to substructure will likely overestimate
the substructure fraction in massive galaxies.

\end{abstract}

\begin{keywords}
gravitational lensing
\end{keywords}

@@

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
However, observations of the Local Group show many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane and the latest discovery of new dwarf galaxies \citep{DES15,Kop15}.  
This is the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
understand this discrepancy, it is imperative to build up a large
sample of satellites/subhaloes in galaxies outside the Local Group.
 However, this process is challenging due to the faintness of the satellite
galaxies.  Furthermore, lower-mass satellites may not be able to
retain the gas needed for ongoing star formation \citep[e.g.][]{P11},
rendering them effectively dark.  These factors make gravitational
lensing a powerful and promising tool for the detection of
substructure.

It was first suggested by \citet{Mao1998} that flux-ratio anomalies
observed in radio-loud multiple images of lensed quasars could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux-ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are neither sensitive to microlensing from
stars, nor to dust extinction. This makes flux-ratio anomalies a promising
tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,N13}.  
%At present, the amount of substructure derived from flux-ratio anomalies
%seems to be disagreement with predictions from numerical simulations, 
%with the former requiring a larger fraction of mass in substructure than
%expected \citep{Xu14}. 
\textbf{At present, the amount of substructures derived from flux-ratio anomalies eases the disagremeent with direct detections and numerical simulations.
\emph{Gravitational imaging technique}, by utilizing the surface brightness distribution of extended arcs and Einstein rings,
has been introduced by \citet{K05} and \citet{V09} and gives the measurements of the fraction of
substructure. The result
is currently in agreement with theoretical expectations \citep{V14a,V12} although the simulation results show less level of flux anomalies than expected \citep{Xu14}.}
While this could be the result of small sample
statistics, it could also be an indication that flux-ratio anomalies
have a different origin than substructure. \textbf{ISM and microlensing both can produce flux anomalies in strong lens systems, but not like substurcture pertubations, the effects from ISM show strong frequency dependence and  microlensing from star-size objects is negligible in radio band. These alternative origins have been ruled out among known radio loud flux anomlous systems which implies detection of substructures \citep{KD04}. }[OTHER POSSIBLE ORIGONS--SIMONA]
%

%While future large-scale surveys, such as the LSST, are expected to
%deliver new large samples of gravitationally lensed quasars, in the
%near future the discovery of new systems using narrow-line quasar
%emission \citep{N14} will provide new invaluable statistical
%perspective on current constraints based on flux-ratio anomalies.  
In this letter, we explore the idea that not all flux-ratio anomalies are
related to the presence of substructure, but that some originate in a
more complex lens galaxy mass distribution than initially
considered. To this end we use new infra-red data from the Strong
lensing at High Angular Resolution Program 
\citep[SHARP;][Fassnacht et al., in prep]{SHARP12, V12}.
The main goal of the SHARP project is to re-observe known
quadruple and Einstein ring lens systems at high angular
resolution by making use of observations with (1) adaptive optics (AO)
on the Keck telescopes, (2) the Hubble Space Telescope, and (3) large
interferometric arrays \citep{SHARP12,V12}. In particular, 
we focus on the B1555+375 lens system\citep{Marlow99} to better
understand the causes of flux-ratio anomalies in gravitational lenses.  This system was
discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
has a pair of merging images that show a strong \textbf{persistent} flux-ratio anomaly at
radio wavelengths.  Follow-up observations ruled out radio propagation
effects as the cause of the anomaly \citep{K03,KD04}.  The B1555+375
system was included in both the observational and theoretical analysis
of \citet{Dalal2002} and \citet{Xu14} and, thus, understanding its
mass distribution is of key importance \textbf{to assess systematics in these statistics}.  
%Our analysis makes use of
%the new information obtained from the latest SHARP infrared imaging.
The paper is organized as follows: the  SHARP data are
introduced in section 2; in section 3 we present the lens model while
the results of this analysis and their implications are discussed in
section 4.

\section{Data Collection \& Reduction}

\begin{figure*}
%\begin{minipage}{140mm}
%\includegraphics[width=140mm]{B1555_gallery.eps}
\includegraphics[width=0.95\textwidth]{B1555_gallery.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3.7 arcsec on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the panels show data from
\textit{HST}/WFPC2 in the F555W band, \textit{HST}/WFPC2 in the F814W band, \textit{HST}/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.
\label{fig:multiband}}
%
%\end{minipage}

\end{figure*}

\subsection{Keck Adaptive Optics Imaging}

The B1555+375 system was observed using the NIRC2 camera on the Keck 2
Telescope on the night of 2012 May 16 UT.  The adaptive optics system
was used, with the corrections derived from the laser guide star and a
$R$=14.4 tip-tilt \textbf{star} that was located 45 arcsec from the lens
system.  The narrow camera mode was used, giving a field of view
of roughly 10 arcsec on a side and a pixel scale of 10~mas.
Six dithered 300~s exposures were obtained in the $K^{\prime}$ band filter.  The
data were reduced with the standard SHARP pipeline, which is a
python-based package that is a refinement of the process described in
\citet{Auger_EELS1}.  A cutout of the final reduced image is shown in
Fig.~\ref{fig:multiband} and again in Fig.~\ref{fig:merlin} with
contours from the MERLIN radio observations of \citet{Marlow99}
overlaid.

There are several notable features in the Keck AO data.
These include the nearly complete lack of emission associated with the
B and D lensed images, as can be seen by comparing the radio contours
to the $K^\prime$-band emission, and faint but clearly visible
emission from what appears to be an edge-on lensing galaxy.

\subsection{Hubble Space Telescope Archival Imaging}

The B1555+375 system was also observed with the \textit{Hubble Space Telescope
(\textit{HST})} in three broad bands.  The optical data were obtained with the
Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands
(GO-8804; PI: E.\ Falco), while the Near Infrared Multi-Object
Spectrograph (NICMOS) was used to observe the system in the $F160W$
band (GO-9744; PI: C.\ Kochanek).  The NICMOS observations were
obtained with the NIC2 camera.  We reduced all of the archival \textit{HST}
data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
  MATT], producing final drizzled images with pixel scales of 50~mas.
The reduced images are shown in Figure~\ref{fig:multiband}.  The lens
system is not detected at high significance in the optical bands, but
is clearly seen in the NICMOS $F160W$ image \textbf{where the edge-on lensing
galaxy clearly stands out.}
\textbf{The lens system is red, with a strong jump in flux between the F814W
(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so 
we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
$z_s =1.5$. This assumption on redshifts is needed for the lens modelling because some lens model parameters contain distance information. However, our choice of redshifts does not affect the predicted magnifications nor flux-ratios.}

The observation details of Keck AO and \textit{HST} imaging are shown in Table 1.

\begin{table}
 \centering
 %\begin{minipage}{140mm}
  \caption{Observational details of the B1555+375 lens system.}
  \begin{tabular}{@{}llccc}

\hline
  Telescope     &      Camera     &  Band & Date &$t_{exp}$ (s) \\

 \hline
   \textit{HST}				&		WFPC2    &  F555W		&	2000/10/09 	&	5200\\
   \textit{HST}				&		WFPC2    &  F814W		&	2000/10/09 &	5200\\
   \textit{HST}				&		NICMOS/NIC2	&	F160W	&	2003/11/02 & 5376\\
   Keck2			&		NIRC2 AO	&   $K^\prime$	& 2012/05/16	&  1800\\
   \hline
\end{tabular}
%\end{minipage}
\end{table}

%===========================================================================

@@

%To model B1555+375, we use the lens modelling code {\tt glafic} \citep{Oguri}.  
\textbf{To model B1555+375, we use the lens modelling code {\tt gravlens} \citep{Kee01}.  
The inputs to the model are the observed image
positions and flux densities measured by the radio observations.
We use the image positions from \citet{Marlow99}, who also presented a singular isothermal ellipsoid
(SIE) model that provided a good fit to the image positions but
does not reproduce the strong flux-ratio anomaly between components A
and B.}  %\citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  
\textbf{The flux measurements are performed by \citet{K03} with a half year monitoring to obtain flux-ratio curves, providing throughout discussions in erros on flux densities.}

Although the flux-ratio anomaly that is observed in the radio data implies there must be some perturbations to the mass model, which may be
caused by substructure in the lensing galaxy, our high-resolution near
infrared imaging suggests another explanation.  In both the $K^\prime$
band adaptive optics data and the \textit{HST} infrared imaging (see 
Fig. 1), the lensing galaxy has a clear edge-on disk component with a
position angle of $\approx 10$ degree.  We therefore model the system
with a disk component in order to see if such a model can explain the
flux-ratio anomaly without the need for substructure.  The edge-on
disk may also explain the system morphology that is observed in the
near infrared imaging.  In particular, neither image B nor image D is
detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
these lensed images lie on or close to the edge-on disk.  Thus, strong
extinction in the disk could cause the non-detection of these
images.[REF B0128 PAPER?--LEON]

As a first trial of modelling, we create a single SIE model to check
the performance of a simple lensing potential. Consistent with
previous studies \citep{Marlow99, Xu14}, a single elliptical
potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
\textbf{The next step is to examine if an edge-on disk can cause similar perturbations in the strong lensing system  which results in flux ratio anomalies within the merging images. Among most of mass profiles, exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk \citep{Kee98}. We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of its edge-on disk in lens modelling. The free parameters of the model are, SIE: velocity dispersion ($\sigma$), centroid positions, ellipticity ($e$), and position angle ($\theta$); exponential disk: intrinsic central density ($\kappa_0$), centroid positions, ellipticity ($e$), position angle ($\theta$), and scale length ($R_d$). Detail definition of mass profiles in {\tt gravlens} can be found in \citet{Kee01}.}
  We have not included a third component such as an external
shear component or NFW halo into our model because the number of constraints provided by the
image positions and fluxes would not be sufficient to constrain such a
model. However, we note that the image not affected by dust (image C)
in the Keck AO data is consistent with negligible shear (i.e. shear
strength $\Gamma_s=0.002$), when modeled with the pixelized technique
of \citet{V09}.
%We then create two separate models of the lensing potential that both
%incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
%and an exponential edge-on disk (SIE+expdisk). In the second model
%the disk is represented as a very elongated SIE component (2-SIE).

To obtain \textbf{the minimum $\chi^2$} [OR BEST-FIT MODEL?--JEN] lens model, we explore the parameter space with the following steps: 
\begin{itemize}
\item Preparation of model starting point: Applying the priori infromation from the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the exponential disk. We then use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile and also the source position. The rest of parameters of exponential disk are set to be the same as the SIE component as the starting point.
\item Best-fit model search: We let all model parameter varies but bind the centroid position of two conponents with a Gaussian prior ($\sigma = 0.05 $ arcsec). Run optimization with amoeba algorithm in {\tt gravlens} interatively to reach the global minimum of $\chi^2$ in paramter space.
\item Markov Chain Monte Carlo: After obtaining the best-fit lens model, we run MCMC to explore the parameter space for the uncertainties.
\end{itemize}
%The smallest $\chi^2$ doesn't necessarily give a physical model. Here are the examples we would like to discard: the ellipticity and the position angle of the disk component are far from what we see in the SHARP AO image, the center positions of two components are too far apart physically, or the positions of the lenses and the source are clearly located outside the Einstein radius in the image.
%(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimization with amoeba algorithm to reach the final best-fit for each model.}

The best-fit model parameters are listed in Table 2 and the lens model is illustrated in Fig. 3. 
%Both of these models produce lensed images with positions and
%fluxes that are good matches to the radio observations.  
%While both of the two component models 
%the 2-SIE version has a somewhat
%better performance than the SIE+expdisk model in reproducing flux
%ratios. 
Tables 3 \& 4 show the comparison between radio data and model predicted image positions and flux ratios.  
\textbf{By adding an elongated exponential disk to a smooth potential model, the SIE+expdisk lens model shows significant improvement on the flux ratios when comparing to the SIE-only model, especially the flux ratio anomaly between the merging images.}

>>>>

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
%\documentclass[a4paper,fleqn,usenatbib]{mnras}
\documentclass[a4paper,fleqn,usenatbib,useAMS]{mnras}
% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
% Depending on your LaTeX fonts installation, you might get better results with one of these:
\usepackage{mathptmx}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

\usepackage{times}
\usepackage{epstopdf}
\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{natbib}
\usepackage{array}
\setlength{\topmargin}{-1.2cm}

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Beware the effect of edge-on discs]{SHARP - II. Beware the effect of edge-on discs when interpreting the anomalous flux-ratios of gravitationally lensed quasars}
\author[Hsueh et al.]{Jen-Wei Hsueh,$^{1}$\thanks{E-mail: jwhsueh@ucdavis.edu} A. N. Other,$^{2}$ A. N. Other,$^{2}$  A. N. Other,$^{2}$ A. N. Other,$^{2}$ A. N. Other,$^{2}$
\newauthor and A. N. Other$^{2}$\\
$^{1}$Department of Physics, University of California, Davis, 1 Shields Ave. Davis, CA 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country\\
$^{3}$Building, Institute, Street Address, City, Code, Country\\
$^{4}$Building, Institute, Street Address, City, Code, Country\\
$^{5}$Building, Institute, Street Address, City, Code, Country\\
$^{6}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

\begin{abstract}
Gravitational lens flux-ratio anomalies provide a powerful technique for measuring dark matter substructure in distant galaxies. However, before using these flux-ratio anomalies to test galaxy formation models, it is imperative to ascertain that the given anomalies are indeed due to the presence of dark matter substructure and not due to some other non-smooth component of the lensing galaxy halo. Here we present the case of CLASS~B1555+375, which has a strong radio-wavelength flux-ratio anomaly, but where the lensing galaxy is also revealed in high resolution infrared imaging with the W. M. Keck-II Telescope and the {\it Hubble Space Telescope} to have a clear edge-on disc component that crosses directly over the pair of images that exhibit the flux-ratio anomaly. We find simple models that include the disc can reproduce the cm-wavelength flux-ratio anomaly without requiring additional dark matter substructure. Although further studies are required, our results suggest the assumption that all flux-ratio anomalies are due to a population dark matter sub-haloes may be incorrect, and analyses that do not account for the full non-smooth component of the lens macro-model will likely overestimate the substructure mass fraction in massive lensing galaxies.
\end{abstract}

\begin{keywords}
gravitational lensing -- quasars: individual CLASS B1555+375 -- cosmology: observations 
\end{keywords}

@@

A common feature of dark-matter only simulations of structure formation is the presence of thousands of sub-haloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}. However, observations of the Local Group show many fewer satellite galaxies than are predicted by the simulations, even when taking into account completeness corrections arising from the limited sky coverage imposed by the Galactic Plane and the latest discoveries of new dwarf galaxies \citep{DES15,Kop15}.  
This is the well-known {\it missing satellite problem} \citep{Klypin1999,Moore1999,S07}. In order to understand this discrepancy, it is imperative to build up a large sample of satellites/subhaloes in galaxies outside the Local Group. However, this process is challenging due to the optical/infrared faintness of the satellite galaxies.  Furthermore, lower-mass satellites may not be able to retain the gas needed for ongoing star formation \citep[e.g.][]{P11}, rendering them effectively dark.

It was first suggested by \citet{Mao1998} that the flux-ratio anomalies observed in the multiple radio-loud images of lensed quasars could be interpreted as a sign of the presence of substructure in lens galaxies. Indeed, small perturbations in the gravitational potential are sufficient to cause flux-ratio anomalies in gravitationally lensed systems \citep{metcalf01,Dalal2002,Bradac02}, particularly for those systems with a close pair of merging images \citep{KD04}. At radio wavelengths, the lensed images are neither sensitive to micro-lensing from stars (\citealt{K03}; although see \citealt{koopmans00}), nor to dust extinction. Also, any variation in the properties of the radio images that are due to propagation effects (e.g. interstellar scattering or free-free absorption) have a well understood frequency dependence that can be identified and accounted for (e.g. \citealt{biggs03,M07,winn04}). This makes the flux-ratio anomalies of radio-loud lensed images a promising tool to detect and measure dark matter substructures in a large sample of distant galaxies \citep{Dalal2002}. However, a recent comparison of the observational data (8 gravitational lens systems with four or more images) with the expectations from a set of cold dark matter simulations, which are also representative of the mass and redshift of the lens galaxies, suggest that there is only a 1--4 per cent probability that the observed flux-ratio distribution is produced only by substructure \citep{Xu14}.

The \emph{gravitational imaging technique}, which alternatively utilizes the surface brightness distribution of extended arcs and Einstein rings to detect low-mass substructures within lensing haloes, was introduced by \citet{K05} and \citet{V09}. This method gives a measurement of the substructure mass fraction for a sample of 10 lensing galaxies that is currently in agreement with the theoretical expectations from cold matter matter simulations \citep{V14a,V12}. The reason for the conflicting results between the flux-ratio anomaly and gravitational imaging techniques is not currently clear. While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than substructure.

In this letter, we explore the idea that not all flux-ratio anomalies are due to the presence of substructure, but that some originate from more complex lens galaxy mass distributions than have initially been considered. To this end, we use new infrared imaging data from the Strong lensing at High Angular Resolution Programme \citep[SHARP;][]{mckean07,lagattuta10,SHARP12, V12}. The main goal of the SHARP project is to re-observe known four-image and Einstein ring lens systems at high angular resolution by making use of observations with (1) adaptive optics (AO) on the W. M. Keck telescope, (2) the {\it Hubble Space Telescope (HST)}, and (3) large radio and mm interferometric arrays.

Here we focus on CLASS B1555+375 \citep{Marlow99}, which was discovered as part of the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2}. B1555+375 has four lensed images with a maximum separation of 426~mas in a fold-configuration, where the two merging lensed images show a strong and persistent flux-ratio anomaly at radio wavelengths; previous radio monitoring observations ruled out microlensing effects as the cause of the anomaly \citep{K03}. As B1555+375 was included in both the observational and theoretical analysis of \citet{Dalal2002} and \citet{Xu14}, understanding its mass distribution is of key importance to assess any systematics with the inferred level of substructure in the lensing halo with the flux-ratio anomaly method. The SHARP imaging data are introduced in Section 2 and we present a revised lens model using these data in Section 3. The results of this analysis and their implications are discussed in Section 4. Note that neither the lens galaxy or lensed source redshift are known for B1555+375, which we assume are at $z_l = 1$ and $z_s = 1.5$, respectively, due to their red colour \citep{Marlow99}. This assumption has no effect on the derived magnifications or flux-ratios of our analysis.

\section{Observations \& Data reduction}

Our dataset consists of optical and infrared imaging taken with the W. M. Keck-II Telescope and the {\it HST}, and high-resolution radio imaging taken with the Very Long Baseline Array (VLBA), which are discussed below and are summarized in Table~\ref{tab:obs}.

\subsection{Keck adaptive optics and {\it HST} imaging}

B1555+375 was observed as part of SHARP using the NIRC2 camera on the W. M. Keck-II Telescope on 2012 May 16.  The AO system was used, with the corrections derived from the laser guide star and a $R=14.4$-mag tip-tilt star that was located $\sim45$~arcsec from the lens.  The narrow camera mode was used, giving a field-of-view of $\sim10$~arcsec on a side and a pixel scale of 10~mas. Six dithered 300~s exposures were obtained in the $K^{\prime}$-band filter.  The data were reduced with the standard SHARP pipeline, which is a python-based package that is a refinement of the process described by \citet{Auger_EELS1}.  A cutout of the final reduced image is shown in Fig.~\ref{fig:multiband} and also in Fig.~\ref{fig:merlin}, where the contours from 5-GHz Multi-Element Radio Link Interferometer Network (MERLIN) imaging by \citet{Marlow99} and 1.66-GHz VLBA imaging (see below) are overlaid.

B1555+375 was also observed with the {\it HST} in three broad bands.  The optical data were obtained with the Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands (GO-8804; PI: Falco), while the Near Infrared Multi-Object Spectrograph (NICMOS) was used to observe the system in the F160W band (GO-9744; PI: Kochanek).  The NICMOS observations were obtained with the NIC2 camera.  We reduced all of the archival \textit{HST} data with the standard {\sc multidrizzle} pipeline, producing final drizzled images with pixel-sizes of 50~mas. The reduced images are also shown in Fig.~\ref{fig:multiband}. The lens and the lensed images are not detected at high significance in the optical bands, but are clearly seen in the NICMOS F160W image

There are several notable features in the high-resolution AO and {\it HST} data. These include the nearly complete lack of emission associated with lensed images B and D, as can be seen by comparing the radio contours to the $K^\prime$-band emission, and the faint, but clearly visible emission from what appears to be an edge-on lensing galaxy, with a position angle of $\sim 10$~deg and an ellipticity of $\sim 0.8$. We note that this position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D. Therefore, the lack of emission that is seen from these images is likely due to dust extinction.

\subsection{Very Long Baseline Array imaging}

B1555+375 was observed with the 10 telescopes of the VLBA at a central observing frequency of 1.66 GHz on 2000 March 21 (BN0009; PI: Norbury). The data were recorded at 128 Mbits~s$^{-1}$ and then correlated to produce two spectral windows with 8 MHz bandwidth, 16 channels and both circular polarizations (RR and LL). The observations were phase referenced using J1544+398 every 3 min over the total observing time of 3 h. The data were reduced in the standard manner using the {\sc vlbaprocs} analysis pipeline that is part of the Astronomical Image Processing Software (AIPS). Imaging was done with the {\sc clean} algorithm in AIPS using natural weighting of the visibilities, and restored using an elliptical beam of size $9.7 \times 6.9$~mas at a position angle of $-7.6$~degr east of north. The final map has an rms of 78~$\mu$Jy~beam$^{-1}$ and is also shown in Fig.~\ref{fig:merlin}.

We find that lensed images A and B have been resolved into a gravitational arc that is $\sim100$~mas in size. Image C is still compact on mas-scales, whereas image D is only marginally detected ($\sim6~\sigma$). We immediately see from the high resolution VLBA imaging that image B has a smaller angular size than image A, which is consistent with a perturbation in the mass model being responsible for the flux-ratio anomaly (recall that gravitational lensing conserves surface brightness), as opposed to free-free absorption or interstellar scattering.

\begin{figure*}
\includegraphics[width=0.95\textwidth]{B1555_gallery.eps}
\caption{High-resolution multi-band imaging of B1555+375 with {\it HST}/WFPC2 at F555W (left) and F814W (middle-left), with {\it HST}/NICMOS/NIC2 at F160W (middle-right) and with Keck adaptive optics at $K^\prime$-band (right). All of the panels are 3.7 arcsec on a side and the scale-bar represents 1 arcsec.}
\label{fig:multiband}
\end{figure*}

\begin{table}
\centering
\caption{Summary of the B1555+375 observations.}
\begin{tabular}{llccc}
\hline
Telescope		& Camera			&  Band 		& Date				&$t_{exp}$ (s) \\
\hline
VLBA			&					& 1.66 GHz	& 	2000 Mar 21	& 10800\\
\textit{HST}	& WFPC2    		& F555W		&	2000 Oct 09	& 5200\\
\textit{HST}	& WFPC2    		& F814W		&	2000 Oct 09 	& 5200\\
\textit{HST}	& NICMOS/NIC2	& F160W		&	2003 Nov 02	& 5376\\
Keck-II			& NIRC2 AO		& $K^\prime$	& 	2012 May 16	& 1800\\
\hline
\end{tabular}
\label{tab:obs}
\end{table}

@@

The flux-ratio anomaly and relative sizes of the images at radio-wavelengths implies that there must be some form of perturbation to the gravitational lens mass model, which has thus far been attributed to dark matter substructure within the lensing galaxy or along the line-of-sight to the lensed images \citep{Dalal2002,Xu14}. However, our high-resolution near infrared imaging suggests the intriguing possibility that the mass perturbation could be due to an edge-on disc component within the lens. To test this possibility, we model the system with a disc component in order to see if a plausible mass model can explain the flux-ratio anomaly, without the need for additional substructure.

We use the lens modelling code {\sc gravlens} \citep{Kee01} to model the compact radio components. The inputs to the model are the observed image positions measured from the MERLIN radio observations of \citet{Marlow99} as all of the images are significantly detected in these data. The flux-ratio measurements are taken from \citet{K03}, who used half a year of MERLIN monitoring to obtain flux-ratio curves. In total, there are 11 constraints to the mass model provided by the observational data. As a first trial of modelling, we re-create the singular isothermal ellipsoid (SIE; 7 free parameters) model of \citet{Marlow99} to check the performance of a simple lensing potential. Consistent with previous studies \citep{Marlow99,Xu14}, a single elliptical potential model cannot reproduce the observed flux-ratios in B1555+375 (see Table~\ref{tab:results}; reduced $\chi^2 =~??$).

The next step is to examine if an edge-on disc can cause a physically plausible perturbation in the strong lensing mass model that results in the observed flux ratio anomaly of  merging images A and B. An exponential disc profile best describes the disc component in spiral galaxies because it matches the light distribution \citep{Kee98}. We thus choose a SIE plus an exponential disc model (SIE+ExpDisc) in our study of B1555+375. The free parameters of the model are the SIE velocity dispersion ($\sigma$), centroid position, ellipticity ($e$), and position angle ($\theta$), and the exponential disc intrinsic central density ($\kappa_0$), centroid position, ellipticity ($e$), position angle ($\theta$), and scale length ($R_s$). A Detailed definition of these mass profiles is described by \citet{Kee01}. The source position and flux add three additional model parameters. We have not included a third component such as an external shear or an NFW halo because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model. Significantly deeper observations at a higher bandwidth with current very long baseline interferometric arrays will test more complex models in the future by imaging the extended gravitational arc and more significantly detecting image D.

To obtain the best-fit lens model, we explore the parameter space with the following steps. First, we apply the a priori information from the Keck AO image by setting the ellipticity to $e=0.8$ and the position angle to $\theta=10$ degr for the exponential disc. We then use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile. The rest of the parameters that describe the exponential disc are set to be the same as the SIE component as the starting point. All of the model parameters are then allowed to vary, but we fix the centroid position of the SIE and exponential disc to the infrared positions with a Gaussian prior ($\sigma = 0.05 $~arcsec). The total number of free parameters is ??. After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to explore the parameter space for the uncertainties.

The best-fit model parameters are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:model}. Table \ref{tab:results} also shows the comparison between the observed radio data and the model predicted image positions and flux ratios. We find that by adding an elongated exponential disc to a smooth potential model there is significant improvement in the predicted flux-ratios when compared to the results for the SIE-only model, with a reduced $\chi^2 = ~??$. The positions are all in agreement, and the flux-ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B. The mass model requires that the exponential disc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable. We note that there is a significant 0.036~arcsec offset between the SIE and exponential disc components, which is likely due to there being an additional ellipticity in the model (e.g. from an external shear) that is being partly compensated for by the disc component. Again, more complex mass models that use the full extent of the gravitational arc and the compact lensed images from future high resolution radio imaging will be able confirm this.

\begin{figure}
\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
\caption{High-resolution $K^\prime$-band imaging of B1555+375 with contours from the MERLIN observations of \citet{Marlow99} and the VLBA observations presented here overlaid.}
\label{fig:merlin}
\end{figure}

\begin{figure}
\includegraphics[width=84mm]{gravlens_exp_try5_plot.pdf}
\caption{Observed radio (blue pluses) and model-predicted (red open circles) image positions of B1555+375. The lens-plane critical curves are shown with the blue solid line and the source-plane caustics are shown with the red dash line. The position of the source is at ($-0.1953$, $-0.1494$), which is marked by the red filled circle. The centroid positions of the two mass components of the lens (an SIE and an exponential disc) are marked by the black filled triangles.}
\label{fig:model}
\end{figure}
